Fast solvers for the high-order FEM simplicial de Rham complex \thanks{Submitted to the editors July XX, 2024. \funding{ PDB and PEF were supported by EPSRC grant EP/W026260/1. } }

### 2024-06-14 paper/paper.tex
remove remark

We define a basis for the dual of $V^1_{p, p_E}(K)$ as 
tangential moments along $E\in \text{edges}(\Delta^d)$,
\begin{equation}
   \ell^E_j(v) = (q_j, v\cdot \bt)_E, \quad q_j \in \P_{p_E}(E), 
\end{equation}
and for each sub-entity $S \in \text{faces}(\Delta^d) \cup \text{interior}(\Delta^d)$,
\begin{align}
   \ell^{S,0}_j(v) &= (\grad_S\phi^S_j, v)_{S}, \\
   \ell^{S,1}_j(v) &= (\curl_S\Phi^S_j, \curl_S v)_{S}, \label{eq:hcurl-interior-dofs}
\end{align}
where $\curl_S$ is the tangential curl on $S$,
$\{\phi^S_j\}$ are the $H_0(\grad, S)$ bases constructed in \eqref{eq:hgrad-fdm},
and $\{\curl_S\Phi^S_j\}$ is a basis for $\curl_S \mathbb{B}_{p_S}(\curl, S)$
such that
\begin{equation} \label{eq:hcurl-fdm}
   (\curl_S\Phi^S_j, \curl_S\Phi^S_i)_{S} = \delta_{ij}, \quad
   (\Phi^S_j, \Phi^S_i)_{S} = \lambda_j\delta_{ij}, \quad
   \Phi^S_j\times\bn = 0 \text{ on }\partial S.
\end{equation}
On a 2D face $F$ (or the interior of a 2D cell),
it is not necessary to solve for $\{\Phi^F_j\}$, as the degrees of freedom
\eqref{eq:hcurl-interior-dofs} only involve the scalar-valued 
$\curl_F\Phi^F_j$ which spans $\P_{p_F-1}(F)\setminus\P_0(F)$,
hence the standard $\Ltwo$-orthogonal Dubiner basis may be used in place of $\curl_F\Phi^F_j$.

@@

We define a basis for the dual of $V^2_{p, p_F}(K)$ as normal moments on $F\in
\text{faces}(\Delta^d)$,
\begin{equation}
   \ell^F_j(v) = (q_j, v\cdot \bn)_F, \quad q_j \in \P_{p_F}(F),
\end{equation}
and on the $\text{interior}(\Delta^d) = K$: 
\begin{align}
   \ell^{K,0}_j(v) &= (\curl\Phi^K_j, v)_{K}, \\
   \ell^{K,1}_j(v) &= (\div\Psi^K_j, \div v)_{K}, \label{eq:hdiv-interior-dofs}
\end{align}
where $\{\Phi^K_j\}$ are the $H_0(\curl, S)$ bases constructed in
\eqref{eq:hcurl-fdm}, and $\{\div\Psi^K_j\}$ is a basis for $\div
\mathbb{B}_p(\div, K)$ such that
\begin{equation} \label{eq:hdiv-fdm}
   (\div\Psi^K_j, \div\Psi^K_i)_K = \delta_{ij}, \quad
   (\Psi^K_j, \Psi^K_i)_{K} = \lambda_j\delta_{ij}, \quad
   \Psi^K_j\cdot\bn = 0 \text{ on }\partial K.
\end{equation}
It is not necessary to solve for $\{\Psi^K_j\}$, as the degrees of freedom
\eqref{eq:hdiv-interior-dofs} only involve $\div\Psi^K_j$, 
which spans $\P_{p-1}(K)\setminus\P_0(K)$. Hence the standard
$\Ltwo$-orthogonal Dubiner basis may be used in place of $\div\Psi^K_j$.

@@

The dual bases described above yield a sparse basis for $V^k_p(K)$ only
if $K$ is equilateral.

>>>>

We define a basis for the dual of $V^1_{p, p_E}(K)$ as 
tangential moments along $E\in \text{edges}(\Delta^d)$,
\begin{equation}
   \ell^E_j(v) = (q_j, v\cdot \bt)_E, \quad q_j \in \P_{p_E}(E), 
\end{equation}
and for each sub-entity $S \in \text{faces}(\Delta^d) \cup \text{interior}(\Delta^d)$,
\begin{align}
   \ell^{S,0}_j(v) &= (\grad_S\phi^S_j, v)_{S}, \\
   \ell^{S,1}_j(v) &= (\curl_S\Phi^S_j, \curl_S v)_{S}, \label{eq:hcurl-interior-dofs}
\end{align}
where $\curl_S$ is the tangential curl on $S$,
$\{\phi^S_j\}$ are the $H_0(\grad, S)$ bases constructed in \eqref{eq:hgrad-fdm},
and $\{\curl_S\Phi^S_j\}$ is a basis for $\curl_S \mathbb{B}_{p_S}(\curl, S)$
such that
\begin{equation} \label{eq:hcurl-fdm}
   (\curl_S\Phi^S_j, \curl_S\Phi^S_i)_{S} = \delta_{ij}, \quad
   (\Phi^S_j, \Phi^S_i)_{S} = \lambda_j\delta_{ij}, \quad
   \Phi^S_j\times\bn = 0 \text{ on }\partial S.
\end{equation}

@@

We define a basis for the dual of $V^2_{p, p_F}(K)$ as normal moments on $F\in
\text{faces}(\Delta^d)$,
\begin{equation}
   \ell^F_j(v) = (q_j, v\cdot \bn)_F, \quad q_j \in \P_{p_F}(F),
\end{equation}
and on the $\text{interior}(\Delta^d) = K$: 
\begin{align}
   \ell^{K,0}_j(v) &= (\curl\Phi^K_j, v)_{K}, \\
   \ell^{K,1}_j(v) &= (\div\Psi^K_j, \div v)_{K}, \label{eq:hdiv-interior-dofs}
\end{align}
where $\{\Phi^K_j\}$ are the $H_0(\curl, S)$ bases constructed in
\eqref{eq:hcurl-fdm}, and $\{\div\Psi^K_j\}$ is a basis for $\div
\mathbb{B}_p(\div, K)$ such that
\begin{equation} \label{eq:hdiv-fdm}
   (\div\Psi^K_j, \div\Psi^K_i)_K = \delta_{ij}, \quad
   (\Psi^K_j, \Psi^K_i)_{K} = \lambda_j\delta_{ij}, \quad
   \Psi^K_j\cdot\bn = 0 \text{ on }\partial K.
\end{equation}

@@

On an equilateral simplex, the interior block of the mass and stiffness matrices
is fully diagonal, moreover the interior-interface blocks in the stiffness 
vanish for generally mapped elements.

The dual bases described above yield interior-orthogonal primal bases for $V^k_p(K)$ only
if $K$ is equilateral. For generally mapped triangles, the spectral equivalence constant of
a space decomposition that decouples the interior degrees of freedom should depend on how
far the element departs from being equilateral, i.e., the shape regularity parameter.
